Exploring companies data

### 2021-06-10 companies.Rmd
visualizing latest data cleaned by Paula

>>>>

## Ideas to explore:

- Hotspots of interest within countries
- Commodities within the hotspots driven by land use (high priority cases)
- Explore Allen data and see if one can make linkages to specific diseases
- One can use risk areas to link companies -> hotspots -> disease risk
- Once a subset of companies is identified, go up to shareholders: which ones are more exposed?
